### 2017-02-09 Objects/Objects.tex
Some boring caption stuff

The resolution of the x-- and z--coordinates of the primary vertex were measured in
collisions at $\sqrt{s}=13$ TeV and depend strongly on the number of tracks
associated with the vertex, as figure \ref{fig:objects_tracks_pvres} shows.
~\vspace{-1\baselineskip}
\begin{figure}[h!]
\begin{center}
\subfloat[Resolution in x]{\includegraphics[width=0.5\textwidth]{./Objects/Plots/PVResX.png}}
\subfloat[Resolution in z]{\includegraphics[width=0.5\textwidth]{./Objects/Plots/PVResZ.png}}
\end{center}
\caption{Resolution of the x-- (a) and z--coordinate  (b)
of reconstructed primary vertices
as a function of the scalar sum of the \pT s of the associated tracks, 
measured in 2015 (blue triangles) and 2016 (red squares).
The resolution improves
with higher scalar sum of the \pT s of the associated tracks, which corresponds to larger numbers of tracks \cite{cms-trk-dp}.}
\label{fig:objects_tracks_pvres}
\end{figure}

@@

\begin{figure}[h!]
\begin{center}
\subfloat[$\sigma_{i\eta,i\eta}$]{\includegraphics[width=0.5\textwidth]{./Objects/Plots/Sigmaietaieta.png}}
\subfloat[$1/E_{\text{SC}} - 1/p_{e}$]{\includegraphics[width=0.5\textwidth]{./Objects/Plots/OneoverEminOneoverp.png}}
\end{center}
\caption{$\sigma_{i\eta,i\eta}$ (a) and $1/E_{\text{SC}} - 1/p_{e}$ (b) for real (black points)  and 
misidentified (yellow triangles) electrons in a dataset corresponding to 19.7 fb$^{-1}$
taken at $\sqrt{s} = 8$ TeV, overlaid on the distributions for simulated 
real electrons in purple \cite{cms-elereco-run1}.}
\label{fig:ele_id_vars}
\end{figure}

@@

\begin{figure}[h!]
%\subfloat[CSVv2 distribution]{\includegraphics[width=0.6\textwidth]{./Objects/Plots/CSVDistributionMultijet.pdf}}\\
\includegraphics[width=0.7\textwidth]{./Objects/Plots/CSVSF.png}
\caption{%(a) distribution of CSVv2 discriminant for multijet events in 2.6 fb$^{-1}$ 
%collected at $\sqrt{s} = 13$ TeV and (b) 
The b--tagging scale factors and errors for b--jets in the data sample collected during 2015
as a function of jet \pT~for the medium working point of the CSVv2 discriminant \cite{cms-btag-run2}.}
\label{fig:objects_bjets}
\end{figure}

@@

\begin{figure}[h!]
\begin{center}
\subfloat[\MET~distribution in \Zmm events]{\includegraphics[width=0.5\textwidth]{./Objects/Plots/Met_Data.png}}
\subfloat[\MET~resolution]{\includegraphics[width=0.5\textwidth]{./Objects/Plots/transverse_resolution_npv.png}}
\end{center}
\caption{(a) \MET~distributions comparing MVA \MET~(brown circles) to \ac{PF} \MET~ (black circles) for
\Zmm events, which contain no genuine \MET~, in a sample corresponding to 42 pb$^{-1}$ of data collected at $\sqrt{s}=$\mbox{13 TeV}. The \MET~
values for MVA \MET~ are lower than for \ac{PF} \MET. (b) the \MET~ resolution for \ac{PF} \MET~ in blue and MVA \MET~ in red/brown
circles, as a function of number of vertices. The MVA \MET~ resolution is more stable with increased pile--up \cite{cms-dp-mvamet}.}
\label{fig:objects_mvamet}
\end{figure}

@@

\begin{figure}[h!]
\begin{center}
\subfloat[Isolation performance]{\includegraphics[width=0.5\textwidth]{./Objects/Plots/TauEfficiencyIsol.pdf}}\\
\subfloat[Real $\Pgt_{h}$ efficiency for anti-electron discriminator]{\includegraphics[width=0.5\textwidth]{./Objects/Plots/TauEfficiencyEle.pdf}}
\subfloat[$\Pe\rightarrow\Pgt_{h}$ fake rate for the anti-electron discriminator]{\includegraphics[width=0.5\textwidth]{./Objects/Plots/TauMisIDEle.pdf}}
\end{center}
\caption{(a) the jet$\rightarrow\Pgt_{h}$ fake rate in QCD \ac{MC} events versus $\Pgt_{h}$ identification
efficiency for \htotautau \ac{MC} events, comparing the MVA-based isolation discriminator in red with the cut-based 
isolation discriminator in pink. Tighter working points give lower hadronic tau identification
efficiencies and lower fake rates, and for the same $\Pgt_{h}$ identification efficiency the fake rate
from the MVA-based discriminator is lower than from the cut-based discriminator. (b) The real $\Pgt_{h}$ identification
efficiency for different working points of the anti-electron discriminator, as a function of the \pT~of the $\Pgt_{h}$, and (c)
the $\Pe\rightarrow\Pgt_{h}$ fake rate for different working points of the anti-electron discriminator, as a function of
the \pT~of the \Pe.}
\label{fig:tau_efficiency}
\end{figure}
The anti--muon discriminator is a cut-based discriminant, for which a loose and a tight working
point are provided. It is based on variables such as the number of track segments found in various
parts of the muon system around the direction of the $\Pgt_{h}$, and comparisons of calorimeter energy
with the momentum of the leading $\Pgt_{h}$ track.
%\begin{itemize}
%\setlength{\itemsep}{-\baselineskip}
%\item \textbf{Loose:} The $\Pgt_h$ candidate is vetoed by this discriminator if track segments are found in at least two muon stations within a cone of $\Delta R = 0.3$ of the $\Pgt_h$ direction, or if the sum of the electromagnetic and hadronic energy ($E_{\text{ECAL}}+E_{\text{HCAL}}$) is smaller than $0.2\cdot p_{\text{leading track}}$.
%Otherwise it passes the discriminator.
%\item \textbf{Tight:} The $\Pgt_h$ candidate passes this working point if it passes the loose working point and no hits are present within a cone of $\Delta R=0.3$ of the $\Pgt_h$ direction in the \ac{CSCs},\ac{RPCs} and \ac{DT} in the two outermost muon stations.
%\end{itemize}

>>>>

The resolution of the x-- and z--coordinates of the primary vertex were measured in
collisions at $\sqrt{s}=13$ TeV and depend strongly on the number of tracks
associated with the vertex, as figure \ref{fig:objects_tracks_pvres} shows.
~\vspace{-1\baselineskip}
\begin{figure}[h!]
\begin{center}
\subfloat[Resolution in x]{\includegraphics[width=0.5\textwidth]{./Objects/Plots/PVResX.png}}
\subfloat[Resolution in z]{\includegraphics[width=0.5\textwidth]{./Objects/Plots/PVResZ.png}}
\end{center}
\caption[Resolution of the x- and z- coordinates of reconstructed
primary vertices as a function of the scalar sum of the \pT s of the associated
tracks.]{Resolution of the x-- (a) and z--coordinate  (b)
of reconstructed primary vertices
as a function of the scalar sum of the \pT s of the associated tracks, 
measured in 2015 (blue triangles) and 2016 (red squares).
The resolution improves
with higher scalar sum of the \pT s of the associated tracks, which corresponds to larger numbers of tracks \cite{cms-trk-dp}.}
\label{fig:objects_tracks_pvres}
\end{figure}

@@

\begin{figure}[h!]
\begin{center}
\subfloat[$\sigma_{i\eta,i\eta}$]{\includegraphics[width=0.5\textwidth]{./Objects/Plots/Sigmaietaieta.png}}
\subfloat[$1/E_{\text{SC}} - 1/p_{e}$]{\includegraphics[width=0.5\textwidth]{./Objects/Plots/OneoverEminOneoverp.png}}
\end{center}
\caption[$\sigma_{i\eta,i\eta}$ and $1/E_{\text{SC}}-1/p_{e}$ for real 
and misidentified electrons at 8 TeV, for data and MC]{$\sigma_{i\eta,i\eta}$ (a) and $1/E_{\text{SC}} - 1/p_{e}$ (b) for real (black points)  and 
misidentified (yellow triangles) electrons in a dataset corresponding to 19.7 fb$^{-1}$
taken at $\sqrt{s} = 8$ TeV, overlaid on the distributions for simulated 
real electrons in purple \cite{cms-elereco-run1}.}
\label{fig:ele_id_vars}
\end{figure}

@@

\begin{figure}[h!]
%\subfloat[CSVv2 distribution]{\includegraphics[width=0.6\textwidth]{./Objects/Plots/CSVDistributionMultijet.pdf}}\\
\includegraphics[width=0.7\textwidth]{./Objects/Plots/CSVSF.png}
\caption[The b--tagging scale factors and errors for b--jets in the data sample collected during 2015 as a function of jet \pT~for the medium working point of the CSVv2 discriminant.]{%(a) distribution of CSVv2 discriminant for multijet events in 2.6 fb$^{-1}$ 
%collected at $\sqrt{s} = 13$ TeV and (b) 
The b--tagging scale factors and errors for b--jets in the data sample collected during 2015
as a function of jet \pT~for the medium working point of the CSVv2 discriminant \cite{cms-btag-run2}.}
\label{fig:objects_bjets}
\end{figure}

@@

\begin{figure}[h!]
\begin{center}
\subfloat[\MET~distribution in \Zmm events]{\includegraphics[width=0.5\textwidth]{./Objects/Plots/Met_Data.png}}
\subfloat[\MET~resolution]{\includegraphics[width=0.5\textwidth]{./Objects/Plots/transverse_resolution_npv.png}}
\end{center}
\caption[\MET~distributions comparing MVA \MET~to PF \MET~for
\Zmm events, in a sample corresponding to 42 pb$^{-1}$ of data collected
at $\sqrt{s}=13$ TeV.]{(a) \MET~distributions comparing MVA \MET~(brown circles) to \ac{PF} \MET~ (black circles) for
\Zmm events, which contain no genuine \MET~, in a sample corresponding to 42 pb$^{-1}$ of data collected at $\sqrt{s}=$\mbox{13 TeV}. The \MET~
values for MVA \MET~ are lower than for \ac{PF} \MET. (b) the \MET~ resolution for \ac{PF} \MET~ in blue and MVA \MET~ in red/brown
circles, as a function of number of vertices. The MVA \MET~ resolution is more stable with increased pile--up \cite{cms-dp-mvamet}.}
\label{fig:objects_mvamet}
\end{figure}

@@

\begin{figure}[h!]
\begin{center}
\subfloat[Isolation performance]{\includegraphics[width=0.5\textwidth]{./Objects/Plots/TauEfficiencyIsol.pdf}}\\
\subfloat[Real $\Pgt_{h}$ efficiency for anti-electron discriminator]{\includegraphics[width=0.5\textwidth]{./Objects/Plots/TauEfficiencyEle.pdf}}
\subfloat[$\Pe\rightarrow\Pgt_{h}$ fake rate for the anti-electron discriminator]{\includegraphics[width=0.5\textwidth]{./Objects/Plots/TauMisIDEle.pdf}}
\end{center}
\caption[Figures of the jet$\rightarrow\Pgt_{h}$ fake rate in QCD MC events
versus $\Pgt_{h}$ identification efficiency for \htotautau MC events, the real
$\Pgt_{h}$ identification efficiecny for different working points of the anti-electron discriminator, and the $\Pe\rightarrow\Pgt_{h}$ fake rate for different
working points of the anti-electron discriminator.]{(a) the jet$\rightarrow\Pgt_{h}$ fake rate in QCD \ac{MC} events versus $\Pgt_{h}$ identification
efficiency for \htotautau \ac{MC} events, comparing the MVA-based isolation discriminator in red with the cut-based 
isolation discriminator in pink. Tighter working points give lower hadronic tau identification
efficiencies and lower fake rates, and for the same $\Pgt_{h}$ identification efficiency the fake rate
from the MVA-based discriminator is lower than from the cut-based discriminator. (b) The real $\Pgt_{h}$ identification
efficiency for different working points of the anti-electron discriminator, as a function of the \pT~of the $\Pgt_{h}$, and (c)
the $\Pe\rightarrow\Pgt_{h}$ fake rate for different working points of the anti-electron discriminator, as a function of
the \pT~of the \Pe.}
\label{fig:tau_efficiency}
\end{figure}
The anti--muon discriminator is a cut-based discriminant, for which a loose and a tight working
point are provided. It is based on variables such as the number of track segments found in various
parts of the muon system around the direction of the $\Pgt_{h}$, and comparisons of calorimeter energy
with the momentum of the leading $\Pgt_{h}$ track.
%\begin{itemize}
%\setlength{\itemsep}{-\baselineskip}
%\item \textbf{Loose:} The $\Pgt_h$ candidate is vetoed by this discriminator if track segments are found in at least two muon stations within a cone of $\Delta R = 0.3$ of the $\Pgt_h$ direction, or if the sum of the electromagnetic and hadronic energy ($E_{\text{ECAL}}+E_{\text{HCAL}}$) is smaller than $0.2\cdot p_{\text{leading track}}$.
%Otherwise it passes the discriminator.
%\item \textbf{Tight:} The $\Pgt_h$ candidate passes this working point if it passes the loose working point and no hits are present within a cone of $\Delta R=0.3$ of the $\Pgt_h$ direction in the \ac{CSCs},\ac{RPCs} and \ac{DT} in the two outermost muon stations.
%\end{itemize}

### 2017-02-09 Theory/Theory.tex
Some boring caption stuff

\begin{figure}[h!]
\begin{center}
\subfloat[Gluon fusion]{\includegraphics[width=0.5\textwidth]{./Theory/Figures/feynman_ggH.pdf}}
\subfloat[Vector boson fusion]{\includegraphics[width=0.5\textwidth]{./Theory/Figures/feynman_qqH.pdf}}~\\
\subfloat[W/Z associated production]{\includegraphics[width=0.5\textwidth]{./Theory/Figures/feynman_VH.pdf}}
\subfloat[\ttbar associated production]{\includegraphics[width=0.5\textwidth]{./Theory/Figures/feynman_ttH.pdf}}
\end{center}
\caption{Tree-level Feynman diagrams for the dominant Higgs boson production modes at
the \ac{LHC}.}
\label{fig:theory_smhprod}
\end{figure}

@@

\begin{figure}[h!]
\begin{center}
\subfloat[\ac{SM} H production cross sections]{\includegraphics[width=0.5\textwidth]{./Theory/Figures/plot_13tev_H_sqrt.pdf}}
\subfloat[\ac{SM} H branching ratios]{\includegraphics[width=0.5\textwidth]{./Theory/Figures/SMHiggsBRYR4-square.pdf}}
\end{center}
\caption{(a) \ac{SM} Higgs boson production cross sections at $\sqrt{s} = 13$ TeV and (b) \ac{SM}
Higgs boson branching ratios, for Higgs boson masses between 120 and 130 GeV \cite{YR4}.}
\label{fig:theory_smhxsbr}
\end{figure}

@@

\begin{table}[htp]
\label{tab:mssm_couplings}
\begin{center}
\caption{Tree-level couplings in the MSSM, as multiplicative factors with
respect to the couplings of the Higgs boson in the \ac{SM}.}
\begin{tabular}{p{2cm}p{4cm}p{4cm}p{4cm}}
\toprule
Particle & Coupling to bosons & Coupling to up-type quarks & Coupling to down-type quarks and leptons \\
\midrule
\PHiggsps & 0 & $\cot{\beta}$ & $ \tan{\beta}$\\
\PHiggs & $\cos{\beta-\alpha}$ & $\frac{\sin{\alpha}}{\sin{\beta}}$ & $\frac{\cos{\alpha}}{\cos{\beta}}$\\
\PHiggslight & $\sin{\beta-\alpha}$ & $\frac{\cos{\alpha}}{\sin{\beta}}$ & $-\frac{\sin{\alpha}}{\cos{\beta}}$\\
\bottomrule
\end{tabular}
\label{tab:mssm_couplings}
\end{center}
\end{table}

@@

\begin{figure}[h!]
\begin{center}
\subfloat[gluon fusion production]{\includegraphics[width=0.5\textwidth]{./Theory/Figures/CMS-PAS-HIG-16-037_Figure_001-a.png}}
\subfloat[b-associated production]{\includegraphics[width=0.5\textwidth]{./Theory/Figures/CMS-PAS-HIG-16-037_Figure_001-b.pdf}}
\end{center}
\caption{Tree-level Feynman diagrams of (a) gluon fusion production and (b) b-associated
production of neutral Higgs boson in the MSSM \cite{CMS-PAS-HIG-16-037}.}
\label{fig:production_mssm}
\end{figure}

@@

\begin{figure}[h!]
\begin{center}
\subfloat[\PHiggs]{\includegraphics[width=0.5\textwidth]{./Theory/Figures/typeII2HDMxsbr.png}}
\subfloat[\PHiggsps]{\includegraphics[width=0.5\textwidth]{./Theory/Figures/typeII2HDMxsbrA.png}}
\end{center}
\caption{Inclusive production cross--section times branching ratio for an example
of a type-II \ac{2HDM}, for (a) the \PHiggs boson and (b) the \PHiggsps boson. The
top figures use \tanb=1 and $\cos{(\beta-\alpha)}=-0.11$, the bottom
figures are made for \tanb=10 and $\cos{(\beta-\alpha)}=-0.02$. At low \tanb~the \Htohh and
\AtoZh decays are enhanced for masses up to 350 GeV \cite{2HDM-II}.}
\label{fig:2hdm_Hxsbr}
\end{figure}

@@

\begin{figure}[h!]
\begin{center}
\subfloat[$\sigma(gg\rightarrow \PHiggs)$]{\includegraphics[width=0.5\textwidth]{./Theory/Figures/xs_ggH_mhmodp.pdf}}
\subfloat[$\sigma(gg\rightarrow bb\PHiggs)$]{\includegraphics[width=0.5\textwidth]{./Theory/Figures/xsbbH4F_mhmodp.pdf}}
\end{center}
\caption{Production cross--section of (a) gluon fusion production and (b) b--associated production of the \PHiggs boson
in the $m_{h}^{\text{mod+}}$ scenario. The gluon fusion production cross section is larger at low \tanb, while
the b-associated production cross-section is larger at high \tanb.}
\label{fig:mhmodp_xs}
\end{figure}

@@

\begin{figure}[h!]
\begin{center}
\subfloat[BR($\PHiggs \rightarrow \tau\tau$)]{\includegraphics[width=0.5\textwidth]{./Theory/Figures/brHtautau_mhmodp.pdf}}
\subfloat[BR($\PHiggsps \rightarrow \tau\tau$)]{\includegraphics[width=0.5\textwidth]{./Theory/Figures/brAtautau_mhmodp.pdf}}
\end{center}
\caption{Branching ratio of (a) \PHiggs and (b) \PHiggsps into $\tau\tau$. The branching
ratios into $\tau\tau$ are enhanced at high \tanb.}
\label{fig:mhmodp_br}
\end{figure}

@@

\begin{figure}[h!]
\begin{center}
\subfloat[$m_{h}^{\text{mod}+}$ scenario]{\includegraphics[width=0.5\textwidth]{./Theory/Figures/mh_mhmodp.pdf}}
\subfloat[low \tanb~scenario]{\includegraphics[width=0.5\textwidth]{./Theory/Figures/mh_lowtbhigh.pdf}}
\end{center}
\caption{The mass of the light Higgs boson, \mh, as a function 
of \mA~and \tanb~in (a) the $m_{h}^{\text{mod+}}$ scenario and (b) the low \tanb~scenario. The white areas
indicate masses lower than 122 GeV. The figures shows that
the mass of the light Higgs boson is compatible with 125 GeV over a large
part of the \mA-\tanb~plane in the $m_{h}^{\text{mod+}}$ scenario, except at low \tanb. In the low-\tanb~scenario
the mass of the light Higgs boson is compatible with 125 GeV nearly everywhere.}
\label{fig:mhmodp_mh}
\end{figure}
%\begin{figure}[h!]
%\begin{center}
%\includegraphics[width=0.5\textwidth]{./Theory/Figures/mh_lowtbhigh.png}
%\end{center}
%\caption{Mass of the light Higgs boson in the \mA-\tanb~plane of the low-\tanb~scenario.
%The mass is compatible with 125 GeV nearly everywhere \cite{MSSM-lowtanb}.}
%\label{fig:lowtbhigh_mh}
%\end{figure}
To obtain \mh$\approx$125 GeV over a large part of the parameter
space, 
$M_{\text{SUSY}}$ is not fixed but varies between a few TeV and 100 TeV, while
varying the parameter $X_t$ as:
\begin{equation}
\begin{split}
\tan{\beta} \leq 2 &: \frac{X_t}{M_{\text{SUSY}}} = 2,\\
2 < \tan{\beta} \leq 8.6 &: \frac{X_t}{M_{\text{SUSY}}} = 0.0375\text{tan}^2\beta - 0.7\tan{\beta} + 3.25,\\
8.6 < \tan{\beta} &: \frac{X_t}{M_{\text{SUSY}}} = 0.
\end{split}
\end{equation}
The other trilinear couplings are set to 2 TeV, with $\mu_{\text{MSSM}}$ set to 1.5 TeV and $M_2$ to 2 TeV.

@@

\begin{figure}[h!]
\begin{center}
\subfloat[\Htohh]{\includegraphics[width=0.5\textwidth]{./Theory/Figures/lowtbhigh_hhbr.png}}
\subfloat[\AtoZh]{\includegraphics[width=0.5\textwidth]{./Theory/Figures/lowtbhigh_azhbr.png}}
\end{center}
\caption{Branching fractions of (a) \Htohh and (b) \AtoZh in the low-\tanb~scenario, indicating 
areas where both are significantly enhanced \cite{MSSM-lowtanb}.}
\label{fig:lowtbhigh_br}.
\end{figure}

@@

\begin{figure}[h!]
\begin{center}
\subfloat[$m_{h}^{\text{mod+}}$ scenario]{\includegraphics[width=0.5\textwidth]{./Theory/Figures/CMS-PAS-HIG-16-007_Figure_003-a.pdf}}
\subfloat[hMSSM scenario]{\includegraphics[width=0.5\textwidth]{./Theory/Figures/CMS-PAS-HIG-16-007_Figure_003-b.pdf}}
\end{center}
\caption{Summary of the interpretations of Run 1 \ac{BSM} Higgs searches at \acs{CMS} in (a) the $m_{h}^{\text{mod+}}$ and (b) the
hMSSM scenario. The different coloured areas indicate the observed and expected exclusion from different searches in these
scenarios. The results from \ac{MSSM} Higgs searches with decays into $\tau$ leptons are shown in blue and exclude more of the parameter
space than any of the other searches. The \ac{MSSM} Higgs to $b\bar{b}$ (cyan) and Higgs to $\mu\mu$ (yellow) searches are also sensitive in part
of the high-\tanb~region, with searches for Higgs to WW or ZZ (orange) providing exclusion power at low \tanb~and low mass. In the $m_{h}^{\text{mod+}}$ 
scenario the charged Higgs to $\Pgt\Pgn$ search (magenta) excludes the low mass region for all values of \tanb. Masses below around 300 GeV in the 
hMSSM scenario are excluded instead by constraints from \ac{SM} Higgs boson measurements (magenta). In this scenario small
areas of the low-\tanb~region are also excluded by the searches for $H\rightarrow hh \rightarrow bb\tau\tau$ and $A\rightarrow Zh \rightarrow \ell\ell\tau\tau$ (red)
and the search for $H\rightarrow hh \rightarrow bb\gamma\gamma$ \cite{CMS-PAS-HIG-16-007}.}
\label{fig:bsm_summary}
\end{figure}

>>>>

\begin{figure}[h!]
\begin{center}
\subfloat[Gluon fusion]{\includegraphics[width=0.5\textwidth]{./Theory/Figures/feynman_ggH.pdf}}
\subfloat[Vector boson fusion]{\includegraphics[width=0.5\textwidth]{./Theory/Figures/feynman_qqH.pdf}}~\\
\subfloat[W/Z associated production]{\includegraphics[width=0.5\textwidth]{./Theory/Figures/feynman_VH.pdf}}
\subfloat[\ttbar associated production]{\includegraphics[width=0.5\textwidth]{./Theory/Figures/feynman_ttH.pdf}}
\end{center}
\caption[Tree-level Feynman diagrams for the dominant Higgs production modes at the LHC]{Tree-level Feynman diagrams for the dominant Higgs boson production modes at
the \ac{LHC}.}
\label{fig:theory_smhprod}
\end{figure}

@@

\begin{figure}[h!]
\begin{center}
\subfloat[\ac{SM} H production cross sections]{\includegraphics[width=0.5\textwidth]{./Theory/Figures/plot_13tev_H_sqrt.pdf}}
\subfloat[\ac{SM} H branching ratios]{\includegraphics[width=0.5\textwidth]{./Theory/Figures/SMHiggsBRYR4-square.pdf}}
\end{center}
\caption[SM Higgs boson production cross sections at $\sqrt{s}=13$ TeV and SM Higgs boson branching ratios, for Higgs boson masses between 120 and 130 GeV]{(a) \ac{SM} Higgs boson production cross sections at $\sqrt{s} = 13$ TeV and (b) \ac{SM}
Higgs boson branching ratios, for Higgs boson masses between 120 and 130 GeV \cite{YR4}.}
\label{fig:theory_smhxsbr}
\end{figure}

@@

\begin{table}[htp]
\label{tab:mssm_couplings}
\begin{center}
\caption[Tree-level couplings in the MSSM, as multiplicative factors with respect to the couplings of the Higgs boson in the SM]{Tree-level couplings in the MSSM, as multiplicative factors with
respect to the couplings of the Higgs boson in the \ac{SM}.}
\begin{tabular}{p{2cm}p{4cm}p{4cm}p{4cm}}
\toprule
Particle & Coupling to bosons & Coupling to up-type quarks & Coupling to down-type quarks and leptons \\
\midrule
\PHiggsps & 0 & $\cot{\beta}$ & $ \tan{\beta}$\\
\PHiggs & $\cos{\beta-\alpha}$ & $\frac{\sin{\alpha}}{\sin{\beta}}$ & $\frac{\cos{\alpha}}{\cos{\beta}}$\\
\PHiggslight & $\sin{\beta-\alpha}$ & $\frac{\cos{\alpha}}{\sin{\beta}}$ & $-\frac{\sin{\alpha}}{\cos{\beta}}$\\
\bottomrule
\end{tabular}
\label{tab:mssm_couplings}
\end{center}
\end{table}

@@

\begin{figure}[h!]
\begin{center}
\subfloat[gluon fusion production]{\includegraphics[width=0.5\textwidth]{./Theory/Figures/CMS-PAS-HIG-16-037_Figure_001-a.png}}
\subfloat[b-associated production]{\includegraphics[width=0.5\textwidth]{./Theory/Figures/CMS-PAS-HIG-16-037_Figure_001-b.pdf}}
\end{center}
\caption[Tree-level Feynman diagrams of gluon fusion and b-associated production of neutral Higgs bosons in the MSSM]{Tree-level Feynman diagrams of (a) gluon fusion production and (b) b-associated
production of neutral Higgs bosons in the MSSM \cite{CMS-PAS-HIG-16-037}.}
\label{fig:production_mssm}
\end{figure}

@@

\begin{figure}[h!]
\begin{center}
\subfloat[\PHiggs]{\includegraphics[width=0.5\textwidth]{./Theory/Figures/typeII2HDMxsbr.png}}
\subfloat[\PHiggsps]{\includegraphics[width=0.5\textwidth]{./Theory/Figures/typeII2HDMxsbrA.png}}
\end{center}
\caption[Inclusive production cross--section times branching ratio for an example of a type-II 2HDM, for the \PHiggs and \PHiggsps boson.]{Inclusive production cross--section times branching ratio for an example
of a type-II \ac{2HDM}, for (a) the \PHiggs boson and (b) the \PHiggsps boson. The
top figures use \tanb=1 and $\cos{(\beta-\alpha)}=-0.11$, the bottom
figures are made for \tanb=10 and $\cos{(\beta-\alpha)}=-0.02$. At low \tanb~the \Htohh and
\AtoZh decays are enhanced for masses up to 350 GeV \cite{2HDM-II}.}
\label{fig:2hdm_Hxsbr}
\end{figure}

@@

\begin{figure}[h!]
\begin{center}
\subfloat[$\sigma(gg\rightarrow \PHiggs)$]{\includegraphics[width=0.5\textwidth]{./Theory/Figures/xs_ggH_mhmodp.pdf}}
\subfloat[$\sigma(gg\rightarrow bb\PHiggs)$]{\includegraphics[width=0.5\textwidth]{./Theory/Figures/xsbbH4F_mhmodp.pdf}}
\end{center}
\caption[Production cross--sections of  gluon fusion and b--associated
production of the \PHiggs boson in the $m_{h}^{\text{mod+}}$ scenario.]{Production cross--section of (a) gluon fusion production and (b) b--associated production of the \PHiggs boson
in the $m_{h}^{\text{mod+}}$ scenario. The gluon fusion production cross section is larger at low \tanb, while
the b-associated production cross-section is larger at high \tanb.}
\label{fig:mhmodp_xs}
\end{figure}

@@

\begin{figure}[h!]
\begin{center}
\subfloat[BR($\PHiggs \rightarrow \tau\tau$)]{\includegraphics[width=0.5\textwidth]{./Theory/Figures/brHtautau_mhmodp.pdf}}
\subfloat[BR($\PHiggsps \rightarrow \tau\tau$)]{\includegraphics[width=0.5\textwidth]{./Theory/Figures/brAtautau_mhmodp.pdf}}
\end{center}
\caption[Branching ratio of \PHiggs and \PHiggsps into $\tau\tau$.]{Branching ratio of (a) \PHiggs and (b) \PHiggsps into $\tau\tau$. The branching
ratios into $\tau\tau$ are enhanced at high \tanb.}
\label{fig:mhmodp_br}
\end{figure}

@@

\begin{figure}[h!]
\begin{center}
\subfloat[$m_{h}^{\text{mod}+}$ scenario]{\includegraphics[width=0.5\textwidth]{./Theory/Figures/mh_mhmodp.pdf}}
\subfloat[low \tanb~scenario]{\includegraphics[width=0.5\textwidth]{./Theory/Figures/mh_lowtbhigh.pdf}}
\end{center}
\caption[The mass of the light Higgs boson, \mh, as a function of \mA~and
\tanb~in the $m_{h}^{\text{mod+}}$ scenario and the low \tanb~scenario.]{The mass of the light Higgs boson, \mh, as a function 
of \mA~and \tanb~in (a) the $m_{h}^{\text{mod+}}$ scenario and (b) the low \tanb~scenario. The white areas
indicate masses lower than 122 GeV. The figures shows that
the mass of the light Higgs boson is compatible with 125 GeV over a large
part of the \mA-\tanb~plane in the $m_{h}^{\text{mod+}}$ scenario, except at low \tanb. In the low-\tanb~scenario
the mass of the light Higgs boson is compatible with 125 GeV nearly everywhere.}
\label{fig:mhmodp_mh}
\end{figure}
%\begin{figure}[h!]
%\begin{center}
%\includegraphics[width=0.5\textwidth]{./Theory/Figures/mh_lowtbhigh.png}
%\end{center}
%\caption{Mass of the light Higgs boson in the \mA-\tanb~plane of the low-\tanb~scenario.
%The mass is compatible with 125 GeV nearly everywhere \cite{MSSM-lowtanb}.}
%\label{fig:lowtbhigh_mh}
%\end{figure}
To obtain \mh$\approx$125 GeV over a large part of the parameter
space, 
$M_{\text{SUSY}}$ is not fixed but varies between a few TeV and 100 TeV, while
varying the parameter $X_t$ as:
\begin{equation}
\begin{split}
\tan{\beta} \leq 2 &: \frac{X_t}{M_{\text{SUSY}}} = 2,\\
2 < \tan{\beta} \leq 8.6 &: \frac{X_t}{M_{\text{SUSY}}} = 0.0375\text{tan}^2\beta - 0.7\tan{\beta} + 3.25,\\
8.6 < \tan{\beta} &: \frac{X_t}{M_{\text{SUSY}}} = 0.
\end{split}
\end{equation}
The other trilinear couplings are set to 2 TeV, with $\mu_{\text{MSSM}}$ set to 1.5 TeV and $M_2$ to 2 TeV.

@@

\begin{figure}[h!]
\begin{center}
\subfloat[\Htohh]{\includegraphics[width=0.5\textwidth]{./Theory/Figures/lowtbhigh_hhbr.png}}
\subfloat[\AtoZh]{\includegraphics[width=0.5\textwidth]{./Theory/Figures/lowtbhigh_azhbr.png}}
\end{center}
\caption[Branching fractions of \Htohh and \AtoZh in the low-\tanb~scenario.]{Branching fractions of (a) \Htohh and (b) \AtoZh in the low-\tanb~scenario, indicating 
areas where both are significantly enhanced \cite{MSSM-lowtanb}.}
\label{fig:lowtbhigh_br}.
\end{figure}

@@

\begin{figure}[h!]
\begin{center}
\subfloat[$m_{h}^{\text{mod+}}$ scenario]{\includegraphics[width=0.5\textwidth]{./Theory/Figures/CMS-PAS-HIG-16-007_Figure_003-a.pdf}}
\subfloat[hMSSM scenario]{\includegraphics[width=0.5\textwidth]{./Theory/Figures/CMS-PAS-HIG-16-007_Figure_003-b.pdf}}
\end{center}
\caption[Summary of the interpretations of Run 1 BSM Higgs searches at CMS in the $m_{h}^{\text{mod+}} scenario and the hMSSM scenario.]{Summary of the interpretations of Run 1 \ac{BSM} Higgs searches at \acs{CMS} in (a) the $m_{h}^{\text{mod+}}$ and (b) the
hMSSM scenario. The different coloured areas indicate the observed and expected exclusion from different searches in these
scenarios. The results from \ac{MSSM} Higgs searches with decays into $\tau$ leptons are shown in blue and exclude more of the parameter
space than any of the other searches. The \ac{MSSM} Higgs to $b\bar{b}$ (cyan) and Higgs to $\mu\mu$ (yellow) searches are also sensitive in part
of the high-\tanb~region, with searches for Higgs to WW or ZZ (orange) providing exclusion power at low \tanb~and low mass. In the $m_{h}^{\text{mod+}}$ 
scenario the charged Higgs to $\Pgt\Pgn$ search (magenta) excludes the low mass region for all values of \tanb. Masses below around 300 GeV in the 
hMSSM scenario are excluded instead by constraints from \ac{SM} Higgs boson measurements (magenta). In this scenario small
areas of the low-\tanb~region are also excluded by the searches for $H\rightarrow hh \rightarrow bb\tau\tau$ and $A\rightarrow Zh \rightarrow \ell\ell\tau\tau$ (red)
and the search for $H\rightarrow hh \rightarrow bb\gamma\gamma$ \cite{CMS-PAS-HIG-16-007}.}
\label{fig:bsm_summary}
\end{figure}

### 2017-02-09 frontmatter.tex
Updating Hhh section
Adding some more stuff
First round of own comments on detector chapter
Some more updates
Some boring caption stuff

%% Title
\titlepage[Imperial College London]{%
  A dissertation submitted to Imperial College London\\ for the degree of Doctor of Philosophy}

%% Abstract
%\begin{abstract}%[\smaller \thetitle\\ \vspace*{1cm} \smaller {\theauthor}]
  %\thispagestyle{empty}
%\end{abstract}

@@

%% Preface
%\begin{preface}
%\end{preface}

%% ToC
\tableofcontents

>>>>

%% Title
\titlepage[Imperial College London\\ Department of Physics]{
  A dissertation submitted to Imperial College London\\ for the degree of Doctor of Philosophy}

\begin{abstract}[]
The copyright of this thesis rests with the author and is made available under a
Creative Commons Attribution Non-Commercial No Derivatives licence. Researchers
are free to copy, distribute or transmit the thesis on the condition that they
attribute it, that they do not use it for commercial purposes and that they do
not alter, transform or build upon it. For any reuse or redistribution,
researchers must make clear to others the licence terms of this work.
\end{abstract}
%% Abstract
\begin{abstract}%[\smaller \thetitle\\ \vspace*{1cm} \smaller {\theauthor}]
The BLAH BLAH
  %\thispagestyle{empty}
\end{abstract}

@@

%% Preface
%\begin{preface}
%\end{preface}
%% ToC
\tableofcontents
%\listoffigures
%\listoftables
